Quantum Interval-Valued Probability: Measurement and Probability

### 2017-08-24 prop_iop.tex
prop_iop.tex \subsection{Expectation Values for Classical IVPMs} Add a lemma...

>>>>

Finally, we are going to focus on CIVPMs whose range is $\mathscr{I}_{\mathrm{D}}$.

\begin{lemma}For any CIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$
and a random variable~$X=\sum_{i=1}^{N}x_{i}\mathbf{1}_{E_{i}}$,
$\int X\rmd\bar{\mu}$ is a singleton set~$\left\{ x_{i}\right\} $
for some $i$.\end{lemma}

\begin{proof}By lemma~\ref{lemma:QIVPM2QCM}, $\mul$ and $\mur$
are the same CRVPM, and is simply denoted by $\pmeas:\events\rightarrow\left\{ 1,0\right\} $.
By lemma~\ref{lemma:Choquet-Lebesgue}, $\int X\rmd\bar{\mu}=\left\{ \int X\rmd\mu\right\} $.
Since the range of $\pmeas$ is $\left\{ 1,0\right\} $ and $\sum_{i=1}^{N}\pmeas\left(E_{i}\right)=1$,
there is a unique $i_{0}$ such that $\mu\left(E_{i_{0}}\right)=1$.
Therefore, 
\begin{equation}
\int X\rmd\mu\stackrel{\textrm{Equation }(\ref{eq:expectation})}{=}\sum_{i=1}^{N}x_{i}\pmeas\left(E_{i}\right)=x_{i_{0}}\,.\label{eq:expectation-value-eigenvalue-classical}
\end{equation}
\end{proof}
